Application of Network Flow and Linear Programming to Scheduling of Clinicians

### 2019-08-22 paper/paper.results.tex
Minor fixes to wording in simulations

%We begin by evaluating the runtime in a single-division department, with an increasing number of clinicians, over a 1-year time-span. Figure \ref{fig:avg-runtime-clinicians} shows the average runtime in seconds of 10 runs, for different numbers of clinicians, $C = \{5, 10, 15, 25, 50, 100\}$. From the graph, we can see that the LP formulation performs extremely well on a typical hospital department with no more than 30 clinicians [ref \ref{??}], and can even handle busier departments with upwards of 100 clinicians. \\

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_clinicians}
%	\caption{Plot of average runtime for LP with an increasing number of clinicians}
%	\label{fig:avg-runtime-clinicians}
%\end{figure}

%Next we evaluate the effect of increasing the number of departments. Figure \ref{fig:avg-runtime-divisions} shows the average runtime for a department with 10 clinicians, and a range of divisions, $D = \{1, 2, 3\}$. We can see that increasing the number of divisions even by 2 greatly affects the runtime. The LP solver had significant trouble when we increased the number of divisions further, making it impractical to quickly generate schedules for departments with many divisions. \\

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_divisions}
%	\caption{Plot of average runtime for LP with an increasing number of divisions}
%	\label{fig:avg-runtime-divisions}
%\end{figure}

The effect of an increasing number of requests per clinician on the average runtime of the LP solver is shown in figure \ref{fig:avg-runtime-requests}. We executed the program on a single-division department with 10 clinicians, and $R = \abs{\mathcal{WR}} + \abs{\mathcal{BR}} = \{1, 2, 3, 5, 10\}$ non-overlapping requests per clinician. The increase in the number of requests did not affect the runtime of the LP solver, indicating that it can accommodate a lot of flexibility in clinician requests. \\

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_requests}
	\caption{Average runtime for LP with an increasing number of requests per clinician}
	\label{fig:avg-runtime-requests}
\end{figure}

Figure \ref{fig:avg-runtime-blocks} presents the average runtime over 10 runs for an increasing number of 2-week blocks $B = \{26, 52, 78, 104\}$ to simulate a department that generates schedules for a few years in advance. Although here was an increasing trend in the runtime, the solver was able to find an optimal schedule for all time horizons in under XX amount of time. \\ % 'very reasonable amount of time" is vague. what is reasonable? better to give a range in value.

\begin{figure}[h]
	\centering
	\includegraphics[scale=.7]{fig/avg_runtime_blocks}
	\caption{Average runtime for LP with an increasing number of 2-week blocks}
	\label{fig:avg-runtime-blocks}
\end{figure}

>>>>

The effect of an increasing number of requests per clinician on the runtime of the LP solver is shown in figure \ref{fig:avg-runtime-requests}. We executed the program on a department with 10 clinicians offering two services, similar to the department at St. Michael's Hospital. Each clinician had $R = \abs{\mathcal{WR}} + \abs{\mathcal{BR}} = \{???\}$ non-overlapping requests. The increase in the number of requests did not affect the runtime of the LP solver, indicating that it can accommodate a lot of flexibility in clinician requests. \\

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_requests}
%	\caption{Average runtime for LP with an increasing number of requests per clinician}
%	\label{fig:avg-runtime-requests}
%\end{figure}

Figure \ref{fig:avg-runtime-blocks} presents the change in runtime when increasing the number of 2-week blocks $B = \{26, 52, 78, 104\}$ in a department with 10 clinicians offering two services. Although here was an increasing trend in the runtime, the solver was able to find an optimal schedule for all time horizons in under XX amount of time. \\ % 'very reasonable amount of time" is vague. what is reasonable? better to give a range in value.

%\begin{figure}[h]
%	\centering
%	\includegraphics[scale=.7]{fig/avg_runtime_blocks}
%	\caption{Average runtime for LP with an increasing number of 2-week blocks}
%	\label{fig:avg-runtime-blocks}
%\end{figure}
